Inefficient Concessions and Mediation

### 2021-01-29 draft.tex
Fix mediator theorem

\begin{theorem}
\emph{Mediation}
\begin{enumerate}
		\item[(a)] The mediation mechanism $M$ is incentive compatible when the specified concession is at least as large as $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}$.
		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs.
\end{enumerate}
	\label{theorem:med}
\end{theorem}
\emph{Proof:} See Appendix.

high type IC:
$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$

@@

Here was have assumed that the mediator specifies $e=1$, which means that gift giving and receiving cancels out. The left hand side has zero gifts because the low-type player under consideration has truthfully revealed itself to be a low type. The mediator only specifies strictly positive gifts if there are two reports of `High.' Likewise, there are no gifts in the $(1-p)X_{FF}^l$ term on the right because the negotiating partner has made a report of `Low.' This leaves
		$$X_{FF}^l \geq X_{FT}^l.$$
		Expanding, we have
		\[
			\frac{W-D}{1-\de_l} \geq T + \left(\cdot \right) + W + \left(\cdot \right) + \frac{\de_l}{1-\de_l}\left(W+ \left(\cdot \right) -D - \left(\cdot \right) \right)
		\]
There are no gifts on the left hand side and so the payoffs from Table 1 apply. The right hand side has place holders $\left(\cdot\right)$ for the impact of the material value of gifts. On the right hand side, we have only the case where both parties declare themselves to be high types. Both parties are instructed to give efficient gifts. The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the ``Peace'' equilibrium. The low-type player under consideration knows it will defect and end up in a ``War'' equilibrium and so invests entirely in the military. 
%		\begin{multline}
%			W-D \geq 
%			\left(1-\de_l\right) \left[T + \al_2Tg^M + W + \left(1-\al_1\right)Wg_2 \right] \\
%			+ \de_l \left(W + \left(1-\al_1\right)Wg_2-D - \left(1-\al_2\right)Dg^M\right)
%			\label{eq:lowICex}
%		\end{multline}
		\begin{equation}
			W-D \geq 
			\left(1-\de_l\right) \left[T + Tg_h + W + Wg_h \right] + \de_l \left(W + Wg_h -D \right)
			\label{eq:med}
		\end{equation}
Canceling like terms and rearranging, we have
			\[
					0 \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) Tg_h + Wg_h + \left(1 - \de_l \right) D
			\]
			Since we assume throughout that gifts must be non-negative, each of $T, W$ and $D$ are positive and $0 \leq \de_l \leq 1$, this inequality can never hold.	\hfill $\blacksquare$\\
			\\
\emph{Proof of Theorem~\ref{theorem:med}:}\\
For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Theorem~\ref{theorem:med}. So we start from
\begin{equation*}
			W-D \geq 
			\left(1-\de_l\right) \left[T + Teg_h + W + Weg_h \right] + \de_l \left(W + Weg_h -D \right) + peg_h - pg_h
		\end{equation*}
Simplifying, we have
\[
	pg_h\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_h\right) + Weg_h + \left(1 - \de_l \right) D
\]
Gathering the terms involving $g_h$ on the left hand side:
\[
	g_h\left[p\left(1 - e\right) -(1-\de_l)eT -eW \right] \geq \left(T - \de_l T \right) + \left(1 - \de_l \right) D
\]
Isolating $g_h$ on the left hand side and gathering terms, we have 
\begin{equation}
	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)} = g^M
	\label{ex:med3}
\end{equation}
As before, the optimal gift is the one where Expression~\ref{ex:med3} holds with equality. We call this value $g^M$. We see here that $g^M$ depends on $e$, which is also the choice of the mediator \emph{and} that we must have $\overline{e} = p - e \left( p + T - \de_l T + W \right) > 0$ in order for the optimal concession to be both positive and finite. Both the optimal concession increases toward infinity as $e$ approaches $\frac{p}{p + \left(1-\de_l\right) + W}$, which is the value that makes the denominator of $g^M$ equal to 0.

>>>>

\begin{theorem}
\emph{Mediation}
\begin{enumerate}
		\item[(a)] The mediation mechanism $M$ is incentive compatible and individually rational for the low type when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}$ and $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
		\item[(b)] The mediation mechanism $M$ is incentive compatible and individually rational for the high type when the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
\end{enumerate}
	\label{theorem:med}
\end{theorem}
\emph{Proof:} See Appendix.

@@

Here was have assumed that the mediator specifies $e=1$, which means that gift giving and receiving cancels out. The left hand side has zero gifts because the low-type player under consideration has truthfully revealed itself to be a low type. The mediator only specifies strictly positive gifts if there are two reports of `High.' Likewise, there are no gifts in the $(1-p)X_{FF}^l$ term on the right because the negotiating partner has made a report of `Low.' This leaves
		$$X_{FF}^l \geq X_{FT}^l.$$
		Expanding, we have
		\[
			\frac{W-D}{1-\de_l} \geq T + \left(\cdot \right) + W + \left(\cdot \right) + \frac{\de_l}{1-\de_l}\left(W+ \left(\cdot \right) -D - \left(\cdot \right) \right)
		\]
There are no gifts on the left hand side and so the payoffs from Table 1 apply. The right hand side has place holders $\left(\cdot\right)$ for the impact of the material value of gifts. On the right hand side, we have only the case where both parties declare themselves to be high types. Both parties are instructed to give efficient gifts. The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the ``Peace'' equilibrium. The low-type player under consideration knows it will defect and end up in a ``War'' equilibrium and so invests entirely in the military. 
%		\begin{multline}
%			W-D \geq 
%			\left(1-\de_l\right) \left[T + \al_2Tg^M + W + \left(1-\al_1\right)Wg_2 \right] \\
%			+ \de_l \left(W + \left(1-\al_1\right)Wg_2-D - \left(1-\al_2\right)Dg^M\right)
%			\label{eq:lowICex}
%		\end{multline}
		\begin{equation}
			W-D \geq 
			\left(1-\de_l\right) \left[T + Tg_h + W + Wg_h \right] + \de_l \left(W + Wg_h -D \right)
			\label{eq:med}
		\end{equation}
Canceling like terms and rearranging, we have
			\[
					0 \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) Tg_h + Wg_h + \left(1 - \de_l \right) D
			\]
			Since we assume throughout that gifts must be non-negative, each of $T, W$ and $D$ are positive and $0 \leq \de_l \leq 1$, this inequality can never hold.	\hfill $\blacksquare$\\
			\\
\emph{Proof of Theorem~\ref{theorem:med}:}\\
(a) The low type's individual rationality constraint is satisfied trivially: the low type gets the `War' payoff forever outside the mechanism; it also gets the `War' payoff forever \emph{inside} the mechanism while not giving or receiving any concession.

For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Theorem~\ref{theorem:med}. So we start from
\begin{equation*}
			W-D \geq 
			\left(1-\de_l\right) \left[T + Teg_h + W + Weg_h \right] + \de_l \left(W + Weg_h -D \right) + peg_h - pg_h
		\end{equation*}
Simplifying, we have
\[
	pg_h\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_h\right) + Weg_h + \left(1 - \de_l \right) D
\]
Gathering the terms involving $g_h$ on the left hand side:
\[
	g_h\left[p\left(1 - e\right) -(1-\de_l)eT -eW \right] \geq \left(T - \de_l T \right) + \left(1 - \de_l \right) D
\]
The right hand side is positive. If the left hand side were negative, we would have a negative upper bound on the size of the gift. Given the requirement that the gift be non-negative, the low type's incentive constraint cannot be satisfied  in this case. Therefore we must assume that $p > e\left(p+\left(1-\de_l\right)T + W\right)$. Using this to isolate $g_h$ on the left hand side and gathering terms, we have 
\begin{equation}
	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}
	\label{eq:med3}
\end{equation}
If Condition~\ref{eq:med3} is met, the mechanism is incentive compatible for the low type.\\
(b) We now turn to the high type, whose incentive compatibility constraint is
\begin{equation}
	pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h
	\label{eq:med4}
\end{equation}
It is always optimal for the high type to invest in civil society when they truthfully reveal. When a high type misrepresents itself as a low type, the mechanism specifies that gifts are exchanged only when there are two high types. This means that there will be no concessions when a high type lies. This implies that Expression~\ref{eq:med4} is also the individual rationality constraint since outside the mechanism they get the `War' payoff and exchange no concessions.

Thus the constraint for both incentive compatibility and individual rationality is
\begin{equation*}
  \frac{p}{1-\de_h}\left(T + Teg \right) - pg +peg+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \frac{1}{1-\de_h}\left(W-D\right)
\end{equation*}
This simplifies to
\begin{equation*}
  \frac{1}{1-\de_h}\left(T + Teg \right) - g +eg \geq \frac{1	}{1-\de_h}\left(W-D\right)
\end{equation*}
\begin{equation*}
  T + Teg - (1-\de_h)(1-e)g \geq W-D
\end{equation*}
\begin{equation*}
  T + Teg - (1-\de_h)(1-e)g \geq W-D
\end{equation*}
\begin{equation*}
  T + D - W \geq \left[Te - (1-\de_h)(1-e)\right]g 
\end{equation*}
If $Te < (1-\de_h)(1-e)$, this is a negative lower bound on the size of the concession and thus implies no additional restriction. If $Te = (1-\de_h)(1-e)$, there is again no restriction because $T+D >W$ by assumption. If $Te > (1-\de_h)(1-e)$, the mechanism is both individually rational and incentive compatible for the high type when $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}>g$. \hfill $\blacksquare$\\

As before, the optimal gift is the one where Expression~\ref{eq:med3} holds with equality [NOT NECESSARILY BECAUSE OF HIGH TYPE IC]. We call this value $g^M$. We see here that $g^M$ depends on $e$, which is also the choice of the mediator \emph{and} that we must have $\overline{e} = p - e \left( p + T - \de_l T + W \right) > 0$ in order for the optimal concession to be both positive and finite. Both the optimal concession increases toward infinity as $e$ approaches $\frac{p}{p + \left(1-\de_l\right) + W}$, which is the value that makes the denominator of $g^M$ equal to 0.
